A practical look at genetic algorithms

### 2015-11-22 evolutionaryComputation/practicals/report.tex
fixed the GA with help of 2 unit tests

Trap functions were simply wrongly implemented, instead of counting the
ones they gave positional values of the ones in the block and used the
block as a lookup value for that.
\subsection{Uncertainties}
Should the elitism selection use tournement selection?
When precisly do we find the optimal solution?
	Should I wait for convergence or just say a string
	of all ones is good enough?
	Is 1 solution good enough or should all members have
	that solution
	I'm assuming 1 solution and that I can give a string
	of just ones.
How many generations to consider. I chose arbitrarly 10.

>>>>

Trap functions were simply wrongly implemented, instead of counting the
ones they gave positional values of the ones in the block and used the
block as a lookup value for that.

Trap function actually reversed the output. I suspected the trap function
was doing it wrong because all the GA's kept failing, so I added a bunch
of very specific test for each block result which confirmend my suspicion.
The actuall bug was a simple reverse, which meant  the population, slowly
leaned towards 0's instead of 1's. and since my 'solution' is a string
of only ones, the end result is that the bisectional search kept increasing
the population size since now anwser was found and the algoritm wasn't happy.

All valuation functions should return a float instead of an Int.
I don't even understan how I could make such a stupid mistake until the
unit test pointed it out to me. (programming for 6+ years..)

\subsection{Uncertainties}
Should the elitism selection use tournement selection?
When precisly do we find the optimal solution?
	Should I wait for convergence or just say a string
	of all ones is good enough?
	Is 1 solution good enough or should all members have
	that solution
	I'm assuming 1 solution and that I can give a string
	of just ones.
How many generations to consider. I chose arbitrarly 10.
